---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bws

<!-- badges: start -->
<!-- badges: end -->

The goal of bws is to provide a user-friendly and efficient implementation of the Bayesian Weighted Sums (BWS) described by Hamra, Maclehose, Croen, Kauffman, and Newschaffer (2021) with some extensions to work with binary and count response data. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("phuchonguyen/bws")
```
## Example

This is a basic example which shows you how to fit BWS:

```{r example}
library(bws)
## We first need to simulate some data
set.seed(123)
N <- 100
P <- 3
K <- 2
X <- matrix(rnorm(N*P), N, P)
Z <- matrix(rnorm(N*K), N, K)  # confounders
w <- gtools::rdirichlet(1, rep(1, P))
theta0 <- 2
theta1 <- 3
beta <- runif(K, 0.5, 1.5)
y <- theta0 + theta1*tcrossprod(X, w) + Z%*%beta + rnorm(N)
y <- as.vector(y)
## Fitting BWS is simple
fit <- bws::bws(iter = 2000, y = y, X = X, Z = Z,
         # additional arguments for rstan::sampling
         chains = 4, cores = 2, show_messages = FALSE)
```

Since the implementation uses Stan and returns an `rstanfit` object, users can enjoy all the functionalities provided in `rstan` to analyze the fitted model:

```{r}
rstan::traceplot(fit, pars = c("w", "theta1"), inc_warmup = TRUE, nrow = 2)
print(fit, pars = c("w", "theta1"))
rstan::plot(fit)
```

The model inferred the correct weights, which are set to `r paste(round(w,2))` in the simulation.

## Reference:

Hamra, G.B.; Maclehose,
R.F.; Croen, L.; Kauffman, E.M.;
Newschaffer, C. Bayesian Weighted
Sums: A Flexible Approach to
Estimate Summed Mixture Effects. *Int. J. Environ. Res. Public Health* **2021**,
*18*, 1373. https://doi.org/10.3390/ijerph18041373
